---
title: "Analysis of ImComp experiment."
output: html_document
---

Author: Javier Ortiz-Tudela (Goethe Uni)
Started on: 21.09.22
Last updated on: 22.09.22

```{r setup, include=FALSE}
## Load libraries.
library(ggpubr)
library(rstatix)
library(dplyr)

## Set directories
if(Sys.info()["sysname"]=="Linux"){
  main_dir <- "/home/javier/PowerFolders/CD_restart/"
}else{
  main_dir <- "/Users/javierortiz/PowerFolders/CD_restart"
}

# Plotting function
make_plot <- function(df, data_to_plot, title) {
  # Select y axis limits for accuracy
  if(grepl("acc", title, fixed = TRUE)){
    ylim=c(0,1)
  }else{
    ylim=""
  }
  
  ggplot(data = df,
         aes(x = congruity, y = data_to_plot, fill=congruity)) +
    geom_boxplot(position = position_nudge(x = 0, y = 0), alpha = .4)+
    geom_point(size = 1, alpha = 0.3) +
    geom_line(aes(group = participant), alpha = .3) +
    facet_grid(cols = vars(clutter)) + 
    stat_summary(fun= mean, geom="point", shape=20, size=7, color="red", fill="red") +
    ggtitle(title) +
    ylim(ylim) +
    ylab(title) +
    labs(fill='Congruency') +
    theme(plot.title.position = "plot")
}

```

```{r load Exp 1A data, include=FALSE}
# Data dir
data_dir <- paste(main_dir , "versions/sparseVScluttered/Random/", sep="/")

## Which subs?
which_subs = c(1:20)

## Read-in the data
for (c_sub in which_subs){
  # Get subject code
  sub_code <- paste("sub-", sprintf("%02d", c_sub), sep="")
  
  # Since the data is in a CSV file, you can read it with the csvread functi
  filename = paste(sub_code, "_task-sparseVScluttered_merged.csv", sep="")
  temp <- read.csv2(paste(data_dir,  "data/beh", sub_code,filename, sep="/"), sep=",")
    
  if (c_sub == 1){
    exp_data <- temp
  } else{
    exp_data <- rbind(exp_data, temp)
  }
}

# Code
exp_data$clutter[exp_data$scn_type == "cluttered"] <- "cluttered"
exp_data$clutter[exp_data$scn_type != "cluttered"] <- "sparse"
exp_data$order <- "Exp 1A (random)"

# Fix some R stuff
exp_data <- exp_data %>% filter(OvsN == "old")
exp_data$cd_acc <- as.numeric(exp_data$cd_acc)
exp_data$cd_rt <- as.numeric(exp_data$cd_rt)
exp_data$id_acc <- as.numeric(exp_data$id_acc)
exp_data$participant <- as.factor(exp_data$participant)
exp_data$congruity <- as.factor(exp_data$congruity)
exp_data$clutter <- as.factor(exp_data$clutter)

# Store
full_data <- exp_data
```

```{r load Exp 1B data, include=FALSE}
# Data dir
data_dir <- paste(main_dir , "versions/sparseVScluttered/Blocked/", sep="/")

## Which subs?
which_subs = c(1:20)

## Read-in the data
for (c_sub in which_subs){
  # Get subject code
  sub_code <- paste("sub-", sprintf("%02d", c_sub), sep="")
  
  # Since the data is in a CSV file, you can read it with the csvread functi
  filename = paste(sub_code, "_task-sparseVScluttered_merged.csv", sep="")
  temp <- read.csv2(paste(data_dir,  "data/beh", sub_code,filename, sep="/"), sep=",")
    
  if (c_sub == 1){
    exp_data <- temp
  } else{
    exp_data <- rbind(exp_data, temp)
  }
}

# Code
exp_data$clutter[exp_data$scn_type == "cluttered"] <- "cluttered"
exp_data$clutter[exp_data$scn_type != "cluttered"] <- "sparse"
exp_data$order <- "Exp1B (blocked)"

# Fix some R stuff
exp_data <- exp_data %>% filter(OvsN == "old")
exp_data$cd_acc <- as.numeric(exp_data$cd_acc)
exp_data$cd_rt <- as.numeric(exp_data$cd_rt)
exp_data$id_acc <- as.numeric(exp_data$id_acc)
exp_data$participant <- as.factor(exp_data$participant)
exp_data$congruity <- as.factor(exp_data$congruity)
exp_data$clutter <- as.factor(exp_data$clutter)

# Store
full_data <- rbind(full_data, exp_data)
```

## Compute overall performance


```{r}
# Aggregate
agg_data <- full_data %>% 
  group_by(order, participant,  changeness) %>% 
  summarise(mean_acc = mean(cd_acc),
            sd_acc = sd(cd_acc))

# Plot
ggplot(data = agg_data,
       mapping = aes(x=changeness, y = mean_acc, color = changeness)) +
  geom_boxplot() +
  facet_grid(cols = vars(order)) + 
  geom_jitter(shape=10, position=position_jitter(0.2)) +
  ylab("Mean acc") + 
  # ylim(c(0,1)) +
  labs(title = paste("Overall acc"))

```

I am using here a fix threshold of .8 to identify poor performers

```{r}
# Aggregate across changeness
agg_data <- full_data %>%
  group_by(order, participant) %>%
  summarise(mean_acc = mean(cd_acc),
            sd_acc = sd(cd_acc))

# Poor performers
poor_performers <- agg_data$participant[agg_data$mean_acc < 0.8]

# Remove poor performers
full_data <- full_data %>%
  filter(!(participant %in% poor_performers))

# Aggregate
agg_data <- full_data %>% 
  group_by(order, participant, changeness) %>% 
  summarise(mean_acc = mean(cd_acc),
            sd_acc = sd(cd_acc))

# Plot clean sample
ggplot(data = agg_data,
       mapping = aes(x=changeness, y = mean_acc, color = changeness)) +
  geom_boxplot() +
    facet_grid(cols = vars(order)) + 
  geom_jitter(shape=10, position=position_jitter(0.2)) +
  ylab("Mean acc") + 
  ylim(c(0,1.1)) +
  labs(title = paste("Overall acc"))

```
## Compute performance at encoding
After removing bad performers, we can aggregate by congruity and scene type to
look at performance.

```{r}
# Aggregate
agg_data <- full_data %>% 
  filter(changeness == "change") %>% 
  group_by(order, participant, congruity, clutter) %>% 
  summarise(mean_acc = mean(cd_acc),
            sd_acc = sd(cd_acc))

# Plot
make_plot(agg_data, agg_data$mean_acc, "Mean acc by congruity")

```
And now look at performance as RTs
```{r}
# Aggregate
agg_data <- full_data %>% 
  filter(changeness == "change", cd_acc == 1) %>% 
  group_by(order, participant, congruity, clutter) %>% 
  summarise(mean_rt = mean(cd_rt, na.rm = T),
            sd_rt = sd(cd_rt, na.rm = T))

# Plot
make_plot(agg_data, agg_data$mean_rt, "Mean RT by congruity")

```

## Detection efficiency
Let's compute the detection efficiency index
```{r}
# Compute as acc/RT
agg_data <- full_data %>% 
  filter(changeness == "change") %>% 
  group_by(order, participant, congruity, clutter) %>% 
  summarise(mean_acc = mean(cd_acc), sd_acc = sd(cd_acc),
            mean_rt = mean(cd_rt, na.rm = T), sd_rt = sd(cd_rt, na.rm = T)) %>% 
  mutate(eff_ind = mean_acc/mean_rt) %>% 
  ungroup()


# Plot
make_plot(agg_data, agg_data$eff_ind, "Mean efficiency by congruity")
 
```

## Compute rANOVA
I will compute a 2x2 repeated measures ANOVA with scene-object congruity (congruent vs. incongruent) and trial type (cluttered vs. sparse) as within-subjects factors.
```{r}
# Need to select only the to-be-used columns
data_to_stat <-  subset(x = agg_data, select = c(participant, order, congruity, clutter, eff_ind))

# Run ANOVA
res.aov <- anova_test(data = data_to_stat, dv = eff_ind, wid = participant, within = c(congruity, clutter), between = order)
get_anova_table(res.aov)

# Pair-wise comparisons
pwc <- data_to_stat %>%
  group_by(clutter) %>% 
  pairwise_t_test(
    eff_ind ~ congruity, paired = TRUE,
    p.adjust.method = "bonferroni"
  )
pwc

```

# Identification
```{r}
# Aggregate
agg_data <- full_data %>% 
  filter(changeness == "change") %>% 
  filter(cd_acc == 1) %>% 
  group_by(order, participant, congruity, clutter) %>% 
  summarise(mean_id = mean(id_acc, na.rm = T),
            sd_id = sd(id_acc, na.rm = T)) %>% 
  ungroup()

# Plot
make_plot(agg_data, agg_data$mean_id, "Mean identification accuracy by congruity")

```

## Compute rANOVA

```{r}
# Need to select only the to-be-used columns
data_to_stat <-  subset(x = agg_data, select = c(order, participant, congruity, clutter, mean_id))

# Run ANOVA
res.aov <- anova_test(data = data_to_stat, dv = mean_id, wid = participant, within = c(congruity, clutter), between = order)
get_anova_table(res.aov)

# Pair-wise comparisons
pwc <- data_to_stat %>%
  group_by(clutter) %>% 
  pairwise_t_test(
    mean_id ~ congruity, paired = TRUE,
    p.adjust.method = "bonferroni"
  )
pwc

```
# Recognition
```{r}
# Aggregate
agg_data <- full_data %>% 
  filter(changeness == "change") %>% 
  filter(cd_acc == 1) %>% 
  group_by(order, participant, congruity, clutter) %>% 
  summarise(mean_rec = mean(rec_acc, na.rm = T)) %>% 
  ungroup()

# Plot
make_plot(agg_data, agg_data$mean_rec, "Mean recognition accuracy by congruity")

```

## Compute rANOVA

```{r}
# Run ANOVA
res.aov <- anova_test(data = agg_data, dv = mean_rec, wid = participant, within = c(congruity, clutter), between = order)
get_anova_table(res.aov)

# Pair-wise comparisons
pwc <- agg_data %>%
  group_by(clutter) %>% 
  pairwise_t_test(
    mean_rec ~ congruity, paired = TRUE,
    p.adjust.method = "bonferroni"
  )
pwc

```

